\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}
\begin{center}
\textbf{Section 33: Finite Fields}
\end{center}

\paragraph{Def:} A field is a \textit{finite field} if it has finite order.

\paragraph{Thm.} Let $E$ be a finite extension of degree $n$ over a finite field $F$. If $F$ has $q$ elements, then $E$ has $q^n$ elements.

\paragraph{Corollary:} If $E$ is a finite field of characteristic $p$, then $E$ contains exactly $p^n$ elements for some positive integer $n$.

\paragraph{Thm.} Let $E$ be a field of $p^n$ elements contained in an algebraic closure $\bar{\mathbb{Z}}_p$ of $\mathbb{Z}_p$. The elements of $E$ are precisely the zeros in $\bar{\mathbb{Z}}_p$ of the polynomial $x^{p^n}-x \in \mathbb{Z}_p[x]$.

\paragraph{Def:} An element $\alpha$ of a field is an \textit{nth root of unity} if $\alpha^n =1$. It is a \textit{primitive nth root of unity} if $\alpha^n = 1$ and $\alpha^m \neq 1$ for $0 < m <n$.

\paragraph{Note:} The nonzero elements of a finite field with $p^n$ elements are all $(p^n-1)$th roots of unity.

\paragraph{Thm.} The multiplicative group $\left \langle F^*, \cdot \right \rangle$ of nonzero elements of a finite field $F$ is cyclic.

\paragraph{Corollary:} A finite extension $E$ of a finite field $F$ is a simple extension of $F$.

\paragraph{Lemma:} If $F$ is a prime of characteristic $p$ with algebraic closure $\bar{F}$, then $x^{p^n}-x$ has $p^n$ distinct zeros in $\bar{F}$.

\paragraph{Freshman's Dream:} If $F$ is a field of prime characteristic $p$, then $(\alpha+\beta)^{p^n} = \alpha^{p^n}+\beta^{p^n}$ for all $\alpha,\beta \in F$ and all positive integers $n$.

\paragraph{Thm.} A finite field $GF(p^n)$ of $p^n$ elements exists for every prime power $p^n$.

\paragraph{Proof Sketch:} We can construct a field by looking for all the zeros of $x^{p^n}-x$ and showing that they form a field of $p^n$ elements.

\paragraph{Corollary:} If $F$ is any finite field, then for every positive integer $n$, there is an irreducible polynomial in $F[x]$ of degree $n$.

\paragraph{Thm.} Let $p$ be a prime and let $n \in \mathbb{Z}^+$. If $E$ and $E'$ are fields of order $p^n$, then $E \simeq E'$.

\paragraph{Note:} This theorem basically says that there is only one finite field of order $p^n$, up to isomorphism.

\end{document}