\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}

\begin{center}
\textbf{Section 49: The Isomorphic Extension Theorem}
\end{center}

\paragraph{Isomorphism Extension Theorem:} Let $E$ be an algebraic extension of a field $F$. Let $\sigma$ be an isomorphism of $F$ onto a field $F'$. Let $\bar{F'}$ be an algebraic closure of $F'$. Then $\sigma$ can be extended to an isomorphism $\tau$ of $E$ onto a subfield of $\bar{F'}$ such that $\tau(a) = \sigma(a)$ for all $a \in F$.

\paragraph{Note:} This theorem allows us to relate extensions of isomorphic fields.

\paragraph{Corollary:} If $E \leq \bar{F}$ is an algebraic extension of $F$ and $\alpha,\beta \in E$ are conjugate over $F$, then the conjugation isomorphism $\psi_{\alpha,\beta}: F(\alpha) \to F(\beta)$, can be extended to an isomorphism of $E$ onto a subfield of $\bar{F}$.

\paragraph{Corollary:} Let $\bar{F}$ and $\bar{F'}$ be two algebraic closures of $F$. Then $\bar{F}$ is isomorphic to $\bar{F'}$ under an isomorphism leaving each element of $F$ fixed.

\paragraph{Note:} Algebraic closure of a field is unique up to isomorphism.

\paragraph{Thm.} Let $E$ be a finite extension of a field $F$. Let $\sigma$ be an isomorphism of $F$ onto a field $F'$, and let $\bar{F'}$ be an algebraic closure of $F'$. Then the nnumber of extensions of $\sigma$ to an isomorphism $\tau$ of $E$ onto a subfield of $\bar{F'}$ is finite, and independent of $F'$, $\bar{F'}$, and $\sigma$. That is, the number of extensions is completely determined by the fields $E$ and $F$.

\paragraph{Def:} Let $E$ be a finite extension of a field $F$. The number of isomorphisms of $E$ onto a subfield of $\bar{F}$ leaving $F$ fixed is the \textit{index} $\{E:F\}$ of $E$ over $F$.

\paragraph{Corollary:} If $F \leq E \leq K$, where $K$ is a finite extension field of the field $F$, then $\{K:F\} = \{K:E\}\{E:F\}$.

\paragraph{Selected Exercises}

\paragraph{10.} Let $E$ be an algebraic extension of a field $F$. Show that every isomorphism of $E$ onto a subfield of $\bar{F}$ leaving $F$ fixed can be extended to an automorphism of $\bar{F}$.

\paragraph{11.} Prove that if $E$ is an algebraic extension of a field $F$, then two algebraic closures $\bar{F}$ and $\bar{E}$ of $F$ and $E$, respectively, are isomorphic.

\paragraph{12.} Prove that the algebraic closure of $\mathbb{Q}(\sqrt{\pi})$ in $\mathbb{C}$ is isomorphic to any algebraic closure of $\bar{\mathbb{Q}}(x)$, where $\bar{\mathbb{Q}}$ is the field of algebraic numbers and $x$ is an indeterminate.

\end{document}