\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\begin{document}

\begin{center}
\textbf{Section 51: Separable Extensions}
\end{center}

\paragraph{Def:} Let $f(x) \in F[x]$. An element $\alpha \in \bar{F}$ such that $f(\alpha) = 0$ is a \textit{zero of multiplicity} $v$, if $v$ is the greatest integer such that $(x-\alpha)^v$ is a factor of $f(x)$ in $\bar{F}[x]$.

\paragraph{Thm.} Let $f(x)$ be irreducible in $F[x]$. Then all the zeros of $f(x)$ in $\bar{F}$ have the same multiplicity.

\paragraph{Corollary:} If $f(x)$ is irreducible in $F[x]$, then $f(x)$ has a factorization in $\bar{F}[x]$ of the form
$$ a\prod_i (x-\alpha_i)^v$$
where the $\alpha_i$ are the distinct zeros of $f(x)$ in $\bar{F}$ and $a \in F$.

\paragraph{Note:} $\{F(\alpha): F\}$ is the number of distinct zeros of $irr(\alpha,F)$.

\paragraph{Thm.} If $E$ is a finite extension of $F$, then $\{E:F\}$ divides $[E:F]$.

\paragraph{Def:} A finite extension $E$ of $F$ is a \textit{separable extension} of $F$ if $\{E:F\} = [E:F]$. An element $\alpha$ of $\bar{F}$ is \textit{separable} over $F$ if $F(\alpha)$ is a separable extension of $F$. An irreducible polynomial of $f(x) \in F[x]$ is \textit{separable over} $F$ if every zero of $f(x)$ in $\bar{F}$ is separable over $F$. 

\paragraph{Thm.} If $K$ is a finite extension of $E$ and $E$ is a finite extension of $F$, that is, $F \leq E \leq K$, then $K$ is separable over $F$ if and only if $K$ is separable over $E$ and $E$ is separable over $F$.

\paragraph{Corollary:} If $E$ is a finite extension of $F$, then $E$ is separable over $F$ if and only if each $\alpha$ in $E$ is separable over $F$. 

\paragraph{Lemma:} Let $\bar{F}$ be an algebraic closure of $F$, and let
$$ f(x) = x^n+a_{n-1}x^{n-1}+ \dots + a_1x + a_0$$
be any monic polynomial in $\bar{F}[x]$. If $(f(x))^m \in F[x]$ and $m \cdot 1 \neq 0$ in $F$, then $f(x) \in F[x]$, that is, all $a_i \in F$.

\paragraph{Def:} A field is \textit{perfect} if every finite extension is a separable extension.

\paragraph{Thm.} Every field of characteristic zero is perfect.

\paragraph{Thm.} Every finite field is perfect.

\paragraph{Primitive Element Theorem:} Let $E$ be a finite separable extension of a field $F$. Then there exists $\alpha \in E$ such that $E = F(\alpha)$. $\alpha$ is called a \textit{primitive element}. That is, a finite separable extension of a field is a simple extension.

\paragraph{Corollary:} A finite extension of a field of characteristic zero is a simple extension.

\paragraph{Selected Exercises}

\paragraph{11.} Prove that if $E$ is an algebraic extension of a perfect field $F$, then $E$ is perfect.

\paragraph{12.} A possibly infinite extension algebraic extension $E$ of a field $F$ is a \textit{separable extension} of $F$ if for every $\alpha in $, $F(\alpha)$ is a separable extension of $F$, in the sense defined. Show that that if $E$ is a separable extension of $F$ and $K$ is a separable extension of $E$, then $K$ is a separable extension of $F$.

\paragraph{13.} Let $E$ be an algebraic extension of a field $F$. Show that the set of all elements in $E$ that are separable over $F$ forms a subfield of $E$, the \textit{separable closure} of $F$ in $E$.

\end{document}